### 2019-09-29 ch7_incgraph/fig/pseudocodeS4.tex
restructure

\begin{algorithmic}
	\Function{CalculateDelta}{Network $G'$, Node $n_0$, Node $n_1$}
		\State \Comment{Assuming an edge $(n_0, n_1)$ has just been added or removed from $G'$}
		\State $\Delta^- \gets \Call{Matrix}{\Call{NumNodes}{G}, 73}$ \Comment{For storing the orbit counts of the removed graphlets}
		\State $\Delta^+ \gets \Call{Matrix}{\Call{NumNodes}{G}, 73}$ \Comment{For storing the orbit counts of the added graphlets}
		\State $B_0 = \{n_0, n_1\}$ \Comment{A blacklist of nodes not to visit anymore}
		\State $e = (n_0, n_1)$ \Comment{Different name for the edge}
		\If{$e \in N'$}
			\State $(m^-, m^+) = (0, 1)$ \Comment{In other words, $m^- = 1$ iff $e \in N$ and $m^+ = 1$ iff $e \in N'$}
		\Else
			\State $(m^-, m^+) = (1, 0)$
		\EndIf
		\State $x_0 = 0$
		\State $(\Delta^+, \Delta^-) = \Call{CountOrbits}{\Delta^+, \Delta^-, (n_0, n_1), x_0, m^-, m^+}$ \Comment{Update delta matrices for current nodes}

		%\For{$n_2 \in \Call{Neighbours}{S_0}$}
		\For{$n_2 \in \bigcup_{i \in \{0, 1\}}\Call{Neighbours}{n_i}$}
			\If{$n_2 \not\in B_0$}
				\State $B_0 = \{n_2\} \bigcup B_0$ \Comment{Add $n_2$ to blacklist $B_0$}
				\State $x_1 = x_0 + \Call{W}{G', (n_0, n_2), 1} + \Call{W}{G', (n_1, n_2), 2}$ \Comment{Calculate edge weights for current nodes}
				\State $(\Delta^+, \Delta^-) = \Call{CountOrbits}{\Delta^+, \Delta^-, (n_0, n_1, n_2), x_1, m^-, m^+}$
				\State $B_1 = B_0$ \Comment{Make a copy for the next iteration depth}
				\For{$n_3 \in \bigcup_{i \in \{0, 1, 2\}}\Call{Neighbours}{n_i}$}
					\If{$n_3 \not\in B_1$}
						\State $B_1 = \{n_3\} \bigcup B_1$
						\State $x_2 = x_1 + \Call{W}{G', (n_0, n_3), 3} + \Call{W}{G', (n_1, n_3), 4} + \Call{W}{G', (n_2, n_3), 5}$
						\State $(\Delta^+, \Delta^-) = \Call{CountOrbits}{\Delta^+, \Delta^-, (n_0, n_1, n_2, n_3), x_2, m^-, m^+}$
						\State $B_2 = B_1$

						\For{$n_4 \in \bigcup_{i \in \{0, 1, 2, 3\}}\Call{Neighbours}{n_i}$}
							\If{$n_4 \not\in B_2$}
								\State $B_2 = \{n_4\} \bigcup B_2$
								\State $x_3 = x_2 + \Sigma_{i \in \{0, 1, 2, 3\}}\Call{W}{G', (n_i, n_4), i+6}$
								\State $(\Delta^+, \Delta^-) = \Call{CountOrbits}{\Delta^+, \Delta^-, (n_0, n_1, n_2, n_3, n_4), x_3, m^-, m^+}$
							\EndIf
						\EndFor
					\EndIf
				\EndFor
			\EndIf
		\EndFor
	\EndFunction
	\Function{CountOrbits}{$\Delta^+$, $\Delta^-$, Nodes $S$, Edgeweights $x$, Modifier $m^-$, Modifier $m^+$}
  \State $L^- = L[x + m^-]$ \Comment{Look up the orbits of the subgraph induced by $S$ in $N$}
			\State $\Delta^-[S, L^-] \pluseq 1$ \Comment{Increment orbit counts of nodes $S$ at positions $L^-$ in $\Delta^-$}
  \State $L^+ = L[x + m^+]$ \Comment{Look up the orbits of the subgraph induced by $S$ in $N'$}
			\State $\Delta^+[S, L^+] \pluseq 1$ \Comment{Increment orbit counts of nodes $S$ at positions $L^+$ in $\Delta^+$}
			\State \Return $(\Delta^-, \Delta^+)$
	\EndFunction
	\Function{W}{Network $G$, Edge $e$, Exponent $i$}
		\State \Return $e \in \Call{Edges}{G} \ ?\  2^i : 0$ \Comment{Return $2^i$ if $G$ contains edge $e$}
	\EndFunction
\end{algorithmic}

>>>>

	\begin{algorithmic}
		\Function{Geometric}{number of nodes $n$, number of edges $e$, \par\hspace*{2.77cm} number of operations $o$, number of dimensions $d=3$}
			\State $P \gets$ Sample $n$ points from a multivariate continuous uniform distribution $U_{d}((0,1)^{d})$
			\State $D \gets$ Calculate distance matrix from $P$
			\State $N_0 \gets \Call{Head}{\Call{ArgSort}{\Call{LowerTriangle}{D}}, e}$ \Comment{Initial network}
			\State $N_p \gets N_0$
			\State $O \gets (\,)$ \Comment{Variable to store the generated operations in}
			\While{$|O| < o$} \Comment{Modify network until $O$ is sufficiently large}
				\State $i \gets $ Sample 1 index from $\{0\,..\,n-1\}$
				\State $P[i] \gets$ Sample 1 point from a $U_{d}((0,1)^{d})$ \Comment{Give node $i$ a new location}
				\State $D[i,] \gets D[,i] \gets $ Calculate new distances between node $i$ and all other nodes
				\State $N_c \gets \Call{Head}{\Call{ArgSort}{\Call{LowerTriangle}{D}}, e}$ \Comment{New network}
				\State $O_a \gets \{(\textrm{ADD}, e) \,|\, e \not\in E(N_p) \wedge e \in E(N_c) \}$ \Comment{Gather added edges}
				\State $O_r \gets \{(\textrm{REM}, e) \,|\, e \in E(N_p) \wedge e \not\in E(N_c) \}$ \Comment{Gather removed edges}
				\State $O \gets O + \Call{Shuffle}{O_a + O_r}$ \Comment{Append new operations to $O$}
				\State $N_p \gets N_c$
			\EndWhile
			\State $O \gets \Call{Head}{O, o}$ 
			\State \Return $(N_0, O)$ \Comment{Return the initial geometric network and $o$ operations}
		\EndFunction
	\end{algorithmic}
